The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-29 article.tex
fixed some typos

  Finally, a signatures fingerprint can be calculated for molecules, to allow
  similarity calculations. This can then be used in QSAR modeling~\cite{signaturefingerprints,
  Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013,Alvarsson2016}.

@@

  A second new design goal was introduced to balance between size restrictions
  of some use cases, such as Java applets, and the rendering functionality. In
  particular, some functionality, even after Modularization, needed considerable
  parts of the CDK library, making creation of a small-sized applet unfeasible.
  Therefore, the rendering API was modularized to allow splitting up rendering
  functionality into modules, with varying CDK dependencies.

>>>>

  Finally, a signature fingerprint can be calculated for molecules, to allow
  similarity calculations. This can then be used in QSAR modeling~\cite{signaturefingerprints,
  Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013,Alvarsson2016}.

@@

  A second new design goal was introduced to balance between size restrictions
  of some use cases, such as Java applets, and the rendering functionality. In
  particular, some functionality, even after modularization, needed considerable
  parts of the CDK library, making creation of a small-sized applet unfeasible.
  Therefore, the rendering API was modularized to allow splitting up rendering
  functionality into modules, with varying CDK dependencies.
